\textcolor{accentcolor}{\textbf{\large {Work Experience}} }\\[0.2cm]

% ----------------------------
% Add main job entries as follows
\textbf{\MakeUppercase{Software Engineer}} \\[0.1cm]
\textit{\textbf{TechCorp}, New York, NY, USA} \hfill \textit{Mar 2020 - Mar 2021}
\begin{itemize}[leftmargin=0.4cm]
    \item Worked as a software engineer at TechCorp, contributing to various software development projects.
\end{itemize}

% ----------------------------
% Add sub-sections for each job as follows (e.g. in case of consultancy/contractor experience)
\begin{tcolorbox}[colback=white, boxrule=0pt, enhanced, borderline west={1pt}{5pt}{accentcolor}, frame hidden]
    \textbf{\MakeUppercase{Data Analyst}} \\[0.1cm]
    \textit{\textbf{DataSolutions}} \hfill \textit{Mar 2020 - Dec 2020}
    \begin{itemize}[leftmargin=1cm]
        \item Conducted data analysis using Python, Excel, and MATLAB to identify trends and insights.
        \item Developed data visualization tools to present findings to stakeholders.
        \item Analyzed large datasets to support decision-making processes.
        \item Presented technical information in a clear and concise manner to clients.
    \end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colback=white, boxrule=0pt, enhanced, borderline west={1pt}{5pt}{accentcolor}, frame hidden]
    \textbf{\MakeUppercase{Quality Assurance Engineer}} \\[0.1cm]
    \textit{\textbf{Innovatech}} \hfill \textit{Dec 2020 - Mar 2021}
    \begin{itemize}[leftmargin=1cm]
        \item Conducted testing and quality assurance for software products.
        \item Developed and executed test cases to ensure software met quality standards.
        \item Identified and resolved software defects, improving product reliability.
        \item Collaborated with development teams to ensure seamless integration and deployment.
    \end{itemize}
\end{tcolorbox}